Многоспиновая запутанность в многоквантовом~ЯМР~с дипольным упорядоченным начальным состоянием

### 2020-07-11 maniscript_ru.tex
Add bibliography into tex file

\bibliographystyle{unsrt}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{bibliography}
\end{document}

>>>>

\bibliographystyle{naturemag}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliography{bibliography}

\begin{thebibliography}{35}
\bibitem{Nielsen_2009}
Nielsen, M. A. and  Chuang, I. L. Quantum Computation and Quantum Information (Cambridge University Press, 2009).

\bibitem{Arute2019}
Arute, F. et al. Quantum supremacy using a programmable superconducting processor. Nature 574,
505–510 (2019).

\bibitem{Baum_1985} 
Baum, J., Munowitz, M., Garroway, A. N. and  Pines, A. Multiple-quantum dynamics in solid state NMR. The Journal of Chemical Physics 83, 2015–2025 (1985).

\bibitem{Furman_2008}
Furman, G. B., Meerovich, V. M. and  Sokolovsky, V. L. Multiple quantum NMR and entanglement dynamics in dipolar coupling spin systems. Physical Review A 78 (2008).

\bibitem{Furman_2009} 
Furman, G. B., Meerovich, V. M. and  Sokolovsky, V. L. Nuclear polarization and entanglement in spin systems. Quantum Information Processing 8, 283–291 (2009).

\bibitem{Fel_dman_2008}
Fel’dman, E. B. and  Pyrkov, A. N. Evolution of spin entanglement and an entanglement witness in multiplequantum NMR experiments. JETP Letters 88, 398–401 (2008).

\bibitem{Fel_dman_2012}
Fel'dman, E. B., Pyrkov, A. N. and  Zenchuk, A. I. Solid-state multiple quantum NMR in quantum information processing: exactly solvable models. Philosophical Transactions of the Royal Society A: Mathematical, Physical and Engineering Sciences 370, 4690–4712 (2012).

\bibitem{G_rttner_2018}
G\"arttner, M., Hauke, P. and  Rey, A. M. Relating out-of-time-order correlations to entanglement via multiplequantum coherences. Physical Review Letters 120, 040402 (2018).

\bibitem{T_th_2014}
T\'oth, G. and  Apellaniz, I. Quantum metrology from a quantum information science perspective. Journal of
Physics A: Mathematical and Theoretical 47, 424006 (2014).

\bibitem{Pezz__2018}
Pezz\'e, L., Smerzi, A., Oberthaler, M. K., Schmied, R. and  Treutlein, P. Quantum metrology with nonclassical states of atomic ensembles. Reviews of Modern Physics 90, 035005 (2018).

\bibitem{Liu_2014}
Liu, J., Xiong, H.-N., Song, F. and  Wang, X. Fidelity susceptibility and quantum fisher information for
density operators with arbitrary ranks. Physica A: Statistical Mechanics and its Applications 410, 167–173 (2014).

\bibitem{Khitrin_1997}
Khitrin, A. Growth of NMR multiple-quantum coherences in quasi-one-dimensional systems. Chemical
Physics Letters 274, 217–220 (1997).

\bibitem{Doronin_2019}
Doronin, S. I., Fel'dman, E. B. and  Lazarev, I. D. Many-particle entanglement in multiple quantum nuclearmagnetic-resonance spectroscopy. Physical Review A 100, 022330 (2019).

\bibitem{Baugh_2001}
Baugh, J., Kleinhammes, A., Han, D., Wang, Q. and  Wu, Y. Confinement effect on dipole-dipole interactions in nanofluids. Science 294, 1505–1507 (2001).

\bibitem{Doronin_2009}
Doronin, S. I., Fedorova, A. V., Fel’dman, E. B. and  Zenchuk, A. I. Multiple quantum NMR dynamics of spin-$\frac 1 2$ carrying molecules of a gas in nanopores. The Journal of Chemical Physics 131, 104109 (2009).

\bibitem{Doronin_2007a}
Doronin, S. I., Fel’dman, E. B., Kuznetsova, E. I., Furman, G. B. and  Goren, S. D. Multiple quantum NMR dynamics in dipolar ordered spin systems. Physical Review B 76, 144405 (2007).

\bibitem{Goldman_1970}
Goldman, M. Spin temperature and nuclear magnetic resonance in solids (Clarendon Press, 1970).

\bibitem{Slichter_1961}
Slichter, C. P. and  Holton, W. C. Adiabatic demagnetization in a rotating reference system. Physical Review 122, 1701–1708 (1961).

\bibitem{Jeener_1967}
Jeener, J. and  Broekaert, P. Nuclear magnetic resonance in solids: Thermodynamic effects of a pair of rf
pulses. Physical Review 157, 232–240 (1967).

\bibitem{Doronin_2007b}
Doronin, S. I., Fel’dman, E. B., Kuznetsova, E. I., Furman, G. B. and  Goren, S. D. Dipolar temperature and multiple-quantum NMR dynamics in dipolar ordered-spin systems. JETP Letters 86, 24–27 (2007).

\bibitem{Doronin_2011}
Doronin, S. I., Fel’dman, E. B. and  Zenchuk, A. I. The multiple quantum NMR dynamics in systems of
equivalent spins with a dipolar ordered initial state. Journal of Experimental and Theoretical Physics 113, 495–501 (2011).

\bibitem{Abragam_1982}
Abragam, A. and  Goldman, M. Nuclear magnetism: Order and disorder (Clarendon Press, United Kingdom,
1982).

\bibitem{Baum_1986}
Baum, J. and  Pines, A. NMR studies of clustering in solids. Journal of the American Chemical Society 108,
7447–7454 (1986).

\bibitem{S_nchez_2014}
S\'anchez, C. M., Acosta, R. H., Levstein, P. R., Pastawski, H. M. and  Chattah, A. K. Clustering and decoherence of correlated spins under double quantum dynamics. Physical Review A 90, 042122 (2014).

\bibitem{Munowitz_1987}
Munowitz, M., Pines, A. and  Mehring, M. Multiple-quantum dynamics in NMR: A directed walk through liouville space. The Journal of Chemical Physics 86, 3172–3182 (1987).

\bibitem{Alvarez_2015}
Alvarez, G. A., Suter, D. and  Kaiser, R. Localization-delocalization transition in the dynamics of dipolarcoupled nuclear spins. Science 349, 846–848 (2015).

\bibitem{Wei_2018}
Wei, K. X., Ramanathan, C. and  Cappellaro, P. Exploring localization in nuclear spin chains. Physical Review Letters 120, 070501 (2018).

\bibitem{Fel_dman_2004}
Fel’dman, E. B. and  Rudavets, M. G. Nonergodic nuclear depolarization in nanocavities. Journal of
Experimental and Theoretical Physics 98, 207–219 (2004).

\bibitem{Fel_dman_1996}
Fel’dman, E. B. and  Lacelle, S. Multiple quantum NMR spin dynamics in one-dimensional quantum spin
chains. Chemical Physics Letters 253, 27–31 (1996).

\bibitem{Zhang_2009}
Zhang, W. et al. NMR multiple quantum coherences in quasi-one-dimensional spin systems: Comparison
with ideal spin-chain dynamics. Physical Review A 80, 052323 (2009).

\bibitem{Girolami_2017}
Girolami, D. and  Yadin, B. Witnessing multipartite entanglement by detecting asymmetry. Entropy 19, 124
(2017).

\bibitem{Helstrom_1976}
Helstrom, C. W. Quantum detection and estimation theory (New York : Academic Press, New York, 1976).

\bibitem{Pezz__2009}
Pezz\'e, L. and Smerzi, A. Entanglement, nonlinear dynamics, and the heisenberg limit. Physical Review
Letters 102, 100401 (2009).

\bibitem{Hyllus_2012}
Hyllus, P. et al. Fisher information and multiparticle entanglement. Physical Review A 85, 022321 (2012).

\bibitem{T_th_2012}
T\'oth, G. Multipartite entanglement and high-precision metrology. Physical Review A 85, 022322 (2012).
\end{thebibliography}

\end{document}
